Untitled

### 2024-10-07 analysis/paper/access-ice.qmd
Re-renders without cache

---
title: "Untitled"
format: gfm
execute: 
  echo: false
  warning: false
  message: false
  cache: true
filters:
  - ../../_extensions/pandoc-ext/abstract-section/abstract-section.lua
  - ../../_extensions/mloubout/critic-markup/critic-markup.lua
  - ../../_extensions/ute/search-replace/search-replace.lua
search-replace:
  +S2: ACCESS-S2
  +S1: ACCESS-S1
  +CDR: CDR
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

  ggplot(aes(lag, value)) +
  geom_line(aes(color = version), linewidth = 1) +
  scale_y_continuous("Variance", 
                     labels = labels_extent_2) +
  # scale_color_models +
  scale_x_continuous("Lag") +
  scale_color_models +
  facet_grid(month ~ component, 
             labeller = labeller(month = labels_month, 
                                 component = c(mean_variance = "Mean variance",
                                               variance_of_mean = "Variance of mean"))) 
```

>>>>

---
title: "Untitled"
format: gfm
execute: 
  echo: false
  warning: false
  message: false
  cache: false
filters:
  - ../../_extensions/pandoc-ext/abstract-section/abstract-section.lua
  - ../../_extensions/mloubout/critic-markup/critic-markup.lua
  - ../../_extensions/ute/search-replace/search-replace.lua
search-replace:
  +S2: ACCESS-S2
  +S1: ACCESS-S1
  +CDR: CDR
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

  ggplot(aes(lag, value)) +

  geom_line(aes(color = version), linewidth = 1) +
  scale_y_continuous("Variance", 
                     labels = labels_extent_2) +
  # scale_color_models +
  scale_x_continuous("Lag", breaks = NULL) +
  scale_color_models +
  facet_grid(month ~ component, 
             labeller = labeller(month = labels_month, 
                                 component = c(mean_variance = "Mean variance",
                                               variance_of_mean = "Variance of mean"))) 
```
